A systematic search for transiting planets in the \KT\ data

### 2015-02-15 ms.tex
todo marks in discussion; acks

To use these distributions to characterize the properties of specific systems,
one should weight our samples by inferred stellar properties...
Perhaps give a specific example here with some detailed discussion or math.

@@

Most importantly, perhaps, the machine and hand vetting leave much to be desired...
list some deficiencies of the vetting.

The completeness and false-positive assessment could be vastly improved...
completeness estimates are not as extensive as desired;
there is essentially no estimate of the non-astrophysical false positive rate.
(There really is no proposal on the table anywhere for getting a false-positive
rate for the non-astrophysical FPs.)

We have not attempted to do any kind of populations analysis...
but presumably \KT\ data will rock this.  In what ways?

\acknowledgments
It is a pleasure to thank
Andrew Vanderburg (Harvard),
Ruth Angus (Oxford), Tom Barclay (Ames), \etal
for helpful contributions to the ideas and code presented here.
DFM, DWH, and DW were partially supported by the National Science Foundation
(grant IIS-1124794),
the National Aeronautics and Space Administration
(grant NNX12AI50G), and the Moore--Sloan Data Science Environment at NYU.
BTM was supported by a National Science Foundation Graduate Research
Fellowship (grant DGE‐1144469).

>>>>

\dfmtodo{
To use these distributions to characterize the properties of specific systems,
one should weight our samples by inferred stellar properties...
Perhaps give a specific example here with some detailed discussion or math.
}

@@

\dfmtodo{
Most importantly, perhaps, the machine and hand vetting leave much to be desired...
list some deficiencies of the vetting.
}

\dfmtodo{
The completeness and false-positive assessment could be vastly improved...
completeness estimates are not as extensive as desired;
there is essentially no estimate of the non-astrophysical false positive rate.
(There really is no proposal on the table anywhere for getting a false-positive
rate for the non-astrophysical FPs.)
}

\dfmtodo{
We have not attempted to do any kind of populations analysis...
but presumably \KT\ data will rock this.  In what ways?
}

\acknowledgments
It is a pleasure to thank
Ruth Angus (Oxford),
Tom Barclay (Ames), and
Andrew Vanderburg (Harvard)
for helpful contributions to the ideas and code presented here.
DFM, DWH, and DW were partially supported by the National Science Foundation
(grant IIS-1124794),
the National Aeronautics and Space Administration
(grant NNX12AI50G), and the Moore--Sloan Data Science Environment at NYU.
BTM was supported by a National Science Foundation Graduate Research
Fellowship (grant DGE‐1144469).
